%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hieu Do - Resume
% 7/26/2016
%
% Reference:
% Debarghya Das (http://debarghyadas.com)

\documentclass[]{hieudo-build}
\usepackage{hyperref}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Siddharth Kale}
{

\urlstyle{same}
    
    
    
	\faEnvelope \href{mailto:siddharth.kale330s@gmail.com}{ Email}\\
	\faGithub \href{https://github.com/Sid330s}{ Github }\\
% 	\faLinkedinSquare \href{https://www.linkedin.com/in/siddharth-kale-936922174/}{ Linkedin}\\
	\faHome { A-16 Primrose Apartment, Baner, Pune, Maharashtra, India - 411005} \\
	\faPhone{  +91 9765237587 }


}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{minipage}[t]{0.34\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 

\subsection{VISHWAKARMA INSTITUTE}
\subsection{OF TECHNOLOGY}
\descript{B.Tech. Computer Engineering}
Graduated in July 2022 \\
{\makebl -Curr. CGPA: 9.49} \\
\sectionsep

\subsection{NOWROSJEE WADIA, Class XII}
Grad. May 2018 \\
HSC - 81.85 \% \\
\sectionsep

\subsection{PPPS, Class X}
Grad. May 2016 \\
SSC - 90.60 \% \\

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Skills}
% \subsection{Programming}
\subsection{Languages:}
Java, C++, Python, JavaScript\\ 

\subsection{Frameworks:}
ReactJS, SpringBoot, ExpressJs \\

\subsection{Databases:}
MongoDB, MySQL \\

\subsection{Tools:}
Git, Docker, AWS \\


% \sectionsep
% \subsection{Languages}
% \location{Native fluency:} English, Vietnamese\\
\sectionsep

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     HACKATHONS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Hackathons}
% HackMIT \textbullet{} hackNY \\
% WearHacks NY \textbullet{} Hackademics VN \\
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ADDITIONAL INFORMATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Achievements} 
\href{https://www.codechef.com/users/siddharth_330s}{\subsection{\underline{4 STAR AT CODECHEF:}}}
1994 Top Rating \\
Feb. Challenge - Global Rank: 52 \\ 
Feb. CookOFF - Global Rank: 101 \\

\href{https://codeforces.com/profile/sid330s}{\subsection{\underline{CODEFORCES SPECIALIST:}}}
1454 Top Rating \\
Round \#715 Global Rank: 904 \\ 
\sectionsep
\subsection{300+ PROBLEMS
\href{https://leetcode.com/user8290n/}{\underline{LeetCode}} + \href{https://auth.geeksforgeeks.org/user/siddharth330s/practice/}{\underline{GeeksForGeeks}}}


\href{https://www.linkedin.com/posts/hackfest-iit-ism-dhanbad_hackfest21-hackisback-imagineinnovateimplement-activity-6794922388480958465-YlZC/}{\subsection{\underline{HACKFEST 2021 TOP 10}}}

\href{https://www.hackerrank.com/siddharthvaidon1}{\subsection{\underline{HACKERRANK 6star}}} 

\href{https://drive.google.com/file/d/1p5sIe6rpAnGlgo3umix68WfPfJ7W4Yt4/view?usp=sharing}{\subsection{\underline{RAKATHON 2021}}}
Went for Finals at Bangalore





%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Coursework}

% Data Structures and Algorithms \\
% Object-Oriented Programming \\
% Database Management Systems \\
% Operating Systems \\

% \sectionsep



% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% %     AWARDS
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \section{Awards} 
% Dean's List\\
% NYU PROMISE Scholarship\\
% Shelby C. Davis Scholarship\\
% President’s Circle Scholarship\\
% \sectionsep

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage} 
\hfill
\begin{minipage}[t]{0.65\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experience}
\workplace{SIEMENS INDUSTRIES SOFTWARE}{Pune, India}\\
\position{Software Engineer Associate}{July 2022 – Present}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item 
Developed and implemented {\makebl -Terraform} \textit{bold text} modules for deploying and managing Teamcenter infrastructure on AWS, reducing deployment time by {\makebl -70\%}
\end{tightemize}
\sectionsep
\position{Intern}{Aug 2021 – June 2022}
\vspace{0.9em} % Hacky fix for awkward extra vertical space
\begin{tightemize}


\item Developed and implemented a Bill Reporting Tool for customer \href{https://www.plm.automation.siemens.com/global/en/products/teamcenter/cloud-plm.html}{\underline{{\makebl -TeamcenterX}}} deployments across various customer AWS accounts and internal dev accounts, resulting in a {\makebl -10\%} reduction in costs through the identification of idle resources, analysis of spending trends, and monitoring of usage patterns. Used:- {\makebl -AWS Lambda, S3, SES, STS, Cloudformation, Gitlab CI/CD}

\item Made a resilient and reliable utility to upgrade Database Engine of existing \href{https://www.plm.automation.siemens.com/global/en/products/teamcenter/cloud-plm.html}{\underline{{\makebl -TeamcenterX}}} customers.
TechStack:- {\makebl - Aurora DB,Python, Boto3 }

\end{tightemize}
\sectionsep


% \runsubsection{The Westminster News} \\
% \descript{Co-Editors-in-Chief (2014) | Layout Editor (2012) }
% \location{Sep 2012 – May 2015 | Simsbury, CT}
% \begin{tightemize}
% \item Led 30+ staff at a 400-student boarding school to publish the monthly school newspaper.
% \item Consulted in layout design and technology application.
% \end{tightemize}
% \sectionsep

% \runsubsection{VietAbroader Organization} \\
% \descript{Program Assistant Manager | VAPedia Associate }
% \location{Mar 2013 – Mar 2014 | Ho Chi Minh City, Vietnam}
% \begin{tightemize}
% \item VietAbroader is a non-profit organization run by Vietnamese students abroad.
% \item Designed the high school content for the VAPedia website.
% \item Assisted in recruiting guest speakers and volunteers for VietAbroader Study-Abroad Conference 2013.
% \end{tightemize}
% \sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\href{https://github.com/Sid330s/Chain4India-Supply-Chain-Model-for-PPE-Kits}{\runsubsection{\underline{CHAIN4INDIA}}}
\descript{Blockchain-based solution for the Medical Equipment Supply Chain.}
\begin{tightemize}
\item Implemented Concurrent {\makebl -RESTful APIs} in Javascript that can interact with {\makebl -Rethink DB} and serve Frontend Web App.
\item Created Interface to Track Medical Equipment using {\makebl -Google Maps API}.
\item Leveraged {\makebl -Hyperledger Sawtooth} for {\makebl -Blockchain} and {\makebl -Docker} for deployment.
\end{tightemize}
\sectionsep

\href{https://github.com/Sid330s/Blockchain-Implementation}{\runsubsection{\underline{Blockchain Implementation}}}
\descript{Blockchain from Scrach.}

\begin{tightemize}
\item Implemented {\makebl -Blockchain Data Structure} with consensus algorithm (Proof Of Work) using {\makebl -Java and Spring Boot}.
\item Was able to establish a network between multiple nodes i.e. {\makebl -Distributed Ledger}.
\end{tightemize}
\sectionsep


\href{https://github.com/Sid330s/Instagram-Clone}{\runsubsection{\underline{INSTAGRAM CLONE}}}
\descript{Social Media Platform}
\begin{tightemize}
\item Built a {\makebl -single-page} web app using {\makebl -React} that offers good UX. Used {\makebl -React} Hooks and {\makebl -Context API}.
\item Implemented {\makebl -Middleware} and {\makebl -JWT based authentication}. Used {\makebl -Cloudinary} for Image Storage Management.
\item Built the whole system using {\makebl -MERN stack}.
\end{tightemize}
\sectionsep


\end{minipage} 

\end{document}  
